Location Classification on Tweets

### 2016-03-08 docs/paper.tex
Finalized the introduction

\title{Location Classification on Tweets}
\author{\name Erdi \c{C}all{\i}  \email e.calli@student.ru.nl}
\maketitle
\begin{abstract}
Previous research on Twitter user location classification is mostly focusing on multi-class prediction. Approaching at the same problem from another perspective, in some cases, it may be enough to answer if someone belongs to a location or not. In this perspective, we have compared some models for predicting tweet locations using Binary and Multi-Class Classification. We have seen that if the problem at hand is reducible to Binary Classification, it is possible to make much better predictions.
\end{abstract}

@@

Proliferation of microblogging platforms, such as Twitter, enabled companies to learn valuable information about their products, customers and businesses. Twitter, introduced the option to include location information on tweets(geotagging) in 2009\footnote{\url{https://blog.twitter.com/2009/location-location-location}}. Since then, many applications(i.e Foursquare) and users started embedding this information to enrich the tweet content. Using geotagged tweets to train classification algorithms, it is proven to be possible to infer tweet locations\cite{cheng2010you}.

Using sentimental analysis\cite{pak2010twitter}, a company can learn if its customers are happy with their products or a political figure can get feedback from his/her voters. The possibilities are endless. Incorporating this information with geolocation may be valuable in lots of situations for politicians, businesses and other parties.

Unfortunately geolocation is not shared in most of the tweets and most of the tweets tagged with location are sent from apps or bots. Also geotags are containing different granularities such as city, neighbourhood or state. Because of those problems most of the data supplied by twitter is filtered out.

In previous studies, this problem has been solved up to a precision as a multi-class classification problem with different algorithms and assumptions. We are introducing binary classification to find the tweets belonging to a specific location.

In this study, different Supervised Learning methods implemented in Scikit Learn\cite{scikit-learn} are tested with different configurations. We have also introduced binary classification on location prediction.\footnote{Source code available at \url{http://www.github.com/xarion/waddle}}

>>>>

\title{Location Classification on Tweets}
\author{\name Erdi \c{C}all{\i}  \email e.calli@student.ru.nl}
\maketitle
\begin{abstract}
% Previous research on Twitter user location classification is mostly focusing on multi-class prediction. Approaching at the same problem from another perspective, in some cases, it may be enough to answer if someone belongs to a location or not. In this perspective, we have compared some models for predicting tweet locations using Binary and Multi-Class Classification. We have seen that if the problem at hand is reducible to Binary Classification, it is possible to make much better predictions.

\end{abstract}

@@

Twitter is an online platform that lets users to share posts with their followers, limited with at most 140 characters, called as tweets. Tweets can be almost anything that we share on internet; a personal message stating our views, a link to an article, a picture and etc.. There are no boundaries except the character limit. In 2009, Twitter introduced an option to include geographic location(geolocation) information on tweets\footnote{\url{https://blog.twitter.com/2009/location-location-location}}. Since then, a lot of twitter users have been sharing their geolocation with their tweets(or geotagging their tweets). Depending on the context of the tweet, having the geolocation may be very valuable. For example a tweet about a Pizza franchise or a political campaign, if geotagged, may point to an improvement with exact location or contribute to the statistics of a specific area. Unfortunately, geolocation of a tweet is not shared by default or in other words, most of the tweets are not geotagged, unless explicitly specified. Inferring the geolocation of a tweet is what this paper is about.

To be able to infer this information, we can try to use linguistic habits shared by the people who are in the same city. As humans, our spatial cognition deals with updating and managing the knowledge about our environment. Spatial cognition changes when we move between environments, but as we stay within the boundaries of a high level environment(i.e. a city), there may be some high level constants that doesn't change. If some of these constants are shared commonly between people, it may lead them to have similar linguistic habits, in this case, textual features in their tweets. If we group the geotagged tweets sent from a city, it may be possible to extract these features, if they exist.

Using similar features, previous research tries to determine the geolocation of a tweet using multi-class classification algorithms. These methods are trying to determine the most likely geolocation for a tweet from a list(e.g. cities in a country). It is sometimes hard to do that, because we need data from all cities. Also the algorithms and the implementations become more complicated. Thus, in cases where we just want to know if someone is from a city or not, this approach becomes unnecessarily heavy. In this research, we are simplifying this problem by using binary classification algorithms, which are trying to determine if a tweet belongs to a location(i.e. New York City) or not.

Revolving around our hypothesis, the research question we're trying to answer is: "Are there textual features in tweets, that are common for people in the same city? If there are, can they help us determine if a tweet is from that city, or not?"
